Supplementary Content

### 2022-02-21 experiments/2_supplement/supplement.Rmd
update supplement

@@

>>>>

## General method

@@

## Effect of abundance change event

**To be completed... waiting for data**

As mentioned in the main report, to avoid very low strain densities, we added 1 unit of density to every biological state variable every 1,000 hours (a slightly different method produced the same results, see the Supplementary Information for details). We also test the effect of making an abundance floor of 1 unit that was implemented every 1,000 hours. I.e. any adundances that were lower than 1 unit were set to 1 unit, every 1,000 hours. As shown below, the results with this floor abundance are the same as when 1 unit is added.

(ref:div-temp-eventdef1) **Left column of panels**: the effect of response trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations. **Right column of panels**: The effect of diversity on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e. delayed the shift to the other state.

```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("experiments/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method_eventdef1.RDS"))
